Energy and exergy analysis of a cruise ship

### 2018-05-24 Manuscript/Manuscript.tex
Updated with the conclusion

>>>>

% Summary of the background
Shipping, similarly to any other industry, is facing challenges in relation to its contribution to climate change. In this context, cruise ships are particularly under scrutiny because of their large impact on the environment, and on their direct connection to their final users.

% What we did in this paper
In this paper, we analyzed the energy system of a cruise ship operating in the Baltic Sea, with the aim of providing a better understanding of how energy is used on board, for what purposes, and with what efficiency. Although these numbers can vary substantially depending on the ship type, size and operating region, the results presented in this paper represent a unique contribution to scientific literature in terms of the detail of the analysis and of the extent of the data available.

% Conclusion: Energy demand share
The results showed that propulsion represents the largest share of the energy demand, as in most ships, but it is less dominant compared to other ship types, as it represents 45\% of the yearly energy demand. Auxiliary electric power and heat represent an approximately equal share of the remaining part (27\% and 28\% respectively), with the largest share of the latter being related to space heating. This is a consequence of the ship being operated in the North of Europe, and results are expected to vary substantially for a ship operating in warmer climates (Mediterranean or Caribbeab Sea, for instance).

% Conclusion: Main sources of exergy destruction
The application of exergy analysis allowed the identification of the main causes for losses of energy quality. In addition to the combustion processes in the main engines and in the boilers, that together contribute to 77\% of the exergy destruction on board, the main potential for improvement was identified in the turbochargers, the exhaust gas boilers (HRSGs), the steam heater in the hot water heat recovery systems, in the HVAC pre-heater and in the sea water cooler. The main basic causes of exergy destruction are hence to be considered the low-load operations of the engines and the mismatch in the operating temperatures of the heat exchangers.

% Conclusion: High system efficiency
The existing ship systems proved to have a high efficiency, at least in relation to other ships of different types. From the results of the energy and exergy analysis it can be concluded that the existing systems already make use of a large share of the waste heat, including that at relatively low temperature that is transferred to the HT cooling systems.

% Conclusion: Potential for improvement 
Despite its good efficiency, the system shows potential for improvement. The fact that both main and auxiliary engines are operated at low load can be compensated with a higher level of electrification of the system, and by the use of batteries. The installation of an ORC can be a solution to use the high-temperature heat of the exhaust gas of the Diesel engines, while low-temperature heat from the Diesel engines could be used, instead of wasted to the sea water cooler, for space heating.
